Path2Vec: An NLP Based Mechanism for File Access Pattern Detection\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-10 master/paper.tex
paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Introduction}
Distributed file systems such as HDFS\cite{HDFS}, GlusterFS[], Ceph\cite{Ceph}, Lustre[] \textcolor{red}{etc}. have been widely deployed as back-end storage systems for parallel/distributed applications.
with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
Caches(burst buffers?) with non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.

\textcolor{red}{Traditional methodoligies: mainly apllying spatial and temporal locality}
For purpose of caching data from lower storage in predictable manner, access pattern detection is essential.
Traditionally, spatial locality and temporal locality are most generally considered facts. 
\textit{Readahead} is a basic mechanism implemented by most file systems\cite{WhyDoes} including linux kernel, which prefeches constant size of data from a opened file to the cache. 
For workloads excuting sequential read, this approach benefits a lot due to the simple and definite pattern.
Unfortunately, many applications especially sientific ones usually do not follow sequential behavior(\textcolor{yellow}{IO acceleration with patter detection}). 
\textcolor{red}{How about small files workloads?}

\textcolor{red}{Curently works}

\textcolor{red}{Briefly introducing your work to address the drawbacks mentioned above.}

The main contributions of this paper can be summerized as follow.
\begin{itemize}
    \item We design and implement a filename embedding model named path2vec, 
    which traverses the user's whole directory and captures naming conventions and semantic relations among directories and files.
    \item A tracing translator is inserted into GlusterFS's storage stack, which is able to collect file access histories and represent these histories as vectors.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{url}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Introduction}
Distributed file systems such as HDFS\cite{HDFS}, GlusterFS\cite{GlusterFS}, Ceph\cite{Ceph}, Lustre\cite{Lustre}, etc., have been widely deployed as back-end storage systems for parallel/distributed applications.
with the data scale continuously increased, I/O access latency between computing nodes and storage servers has become one of the severest bottlenecks in this big data era.
In order to narrow this performance gap, data caching/prefetching in file systems is one of the most well-known optimization techniques.
Caches with high throughput and low latency devices like non-volatile memories(NVMs) and solid state drives(SSDs) are placed at different levels of the I/O stack to hide network and disk latency.

For purpose of caching data from lower storage in predictable manner, access pattern detection is essential.
Traditionally, spatial locality and temporal locality are most generally considered facts. 
\textit{Readahead} is a basic mechanism implemented by most file systems\cite{WhyDoes} including linux kernel, which prefeches constant size of data from a opened file to the cache. 
For workloads excuting sequential read, this approach benefits a lot due to the simple and definite pattern.
Unfortunately, many applications especially sientific ones usually do not access files sequentially.

The main contributions of this paper can be summerized as follow.
\begin{itemize}
    \item We propose an approach to embedd the names of files or directories with Skipgram algorithm, 
    mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
    \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to catch I/O access pattern and encode it with hidden states of the GRU.
    We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.
